---
title: 'DICE'
subtitle: "How Much Is Enough? Exploring Frequency Capping in Social Media Advertising"
author:
- name: Hauke Roggenkamp
  email: Hauke.Roggenkamp@unisg.ch
  orcid: 0009-0005-5176-4718
  corresponding: true
  affiliations:
    - name: Institute of Behavioral Science and Technology, University of St. Gallen
      address: Torstrasse 25
      city: St. Gallen
      country: Switzerland
      postal-code: 9000
date: now
date-format: long
format: 
  html:
    embed-resources: true
    theme: cosmo
    code-line-numbers: true
toc: false
number-sections: false
fig-cap-location: top
execute:
  echo: false
bibliography: ../../../documentation/references.bib
---


# Setup

```{r}
set.seed(42)
```


## Install Packages

```{r install_packages}
#| warning: false
#| output: false

options(repos = c(CRAN = "https://cran.r-project.org")) 


if (!requireNamespace("groundhog", quietly = TRUE)) {
    install.packages("groundhog")
    library("groundhog")
}

pkgs <- c("magrittr", "data.table", "knitr", "stringr", "lubridate", 
          "ggplot2", "patchwork", "ghibli", "sjPlot", "gtsummary", "psych", "effectsize")

groundhog::groundhog.library(pkg = pkgs,
                             date = "2024-01-01")

rm(pkgs)
```


## Layout

```{r layout}
layout <- theme(panel.background = element_rect(fill = "white"),
                legend.key = element_rect(fill = "white"),
                panel.grid.major.y = element_line(colour = "grey", 
                                                  linewidth = 0.25),
                axis.ticks.y = element_blank(),
                panel.grid.major.x = element_blank(),
                axis.line.x.bottom = element_line(colour = "#000000", 
                                                  linewidth = 0.5),
                axis.line.y.left = element_blank(),
                plot.title = element_text(size = rel(1))
)
```

```{r colors}

c_coral     <- "#f27981"
c_yellow    <- "#F2EA79"
c_turquoise <- "#79f2ea"
c_purple    <- "#7981f2"

scale_color_custom_d <- function() {
  scale_color_manual(values = c(c_purple, c_coral, c_turquoise, c_yellow))
}
scale_fill_custom_d <- function() {
  scale_fill_manual(values = c(c_purple, c_coral, c_turquoise, c_yellow))
}
```

## Read Data

```{r read_tweets}
tweet_files <- list.files(path = "../stimuli/LLM-generated",
                          pattern = "brazil")
dt_list <- list()
i <- 1
for(file in tail(x = tweet_files, n = 4)){
  tmp <- data.table::fread(paste0("../stimuli/LLM-generated/", file))
  dt_list[[i]] <- tmp
  i <- i + 1
}

tweets <- data.table::rbindlist(l = dt_list)[nchar(text) < 300]

# rm(list = c("tmp", "i", "tweet_files", "file", "dt_list"))
```

```{r read_usernames}
usernames <- data.table::fread("../stimuli/LLM-generated/users_1718529967.csv")
```

```{r read_ads}
ads_generic <- data.table::fread("../stimuli/ads_generic.csv")
ads_focal   <- data.table::fread("../stimuli/ads_focal.csv")
```

# Data Manipulation

```{r}
length <- 60 # nrow(usernames)
random_draw <- sample(x = tweets[, .N], size = length, replace = FALSE)
```


```{r}
#| warning: false
# Note that usernames will be recycled as 60 > usernames[, .N]

tmp <- cbind(tweets[random_draw],
             usernames)
tmp[, image_url := NA]
tmp[, alt_text := NA]

tmp[, .N, by = topic]
```

## Manual interference

The tweets stored in `tmp` require some human intervention for three reasons:

1. Some LLM-generated posts do not make much sense to a human and need to be deleted.
2. Some posts should be appended by images.
3. The random match between posts and users may not be optimal.

Hence, we save the data, edit it manually and re-read it.

```{r}
data.table::fwrite(x = tmp, file = "../stimuli/to-be-supervized.csv", sep = ";")

rm(tmp)
```

```{r}
tmp <- data.table::fread("../stimuli/supervized.csv")
```


## Back to automation

```{r}
length <- tmp[, .N]
doc_id <- seq(from = 1, to = length, by = 1)
sequence <- seq(from = 1, to = length + 4, by = 1)
sequence <- sequence[-seq(from = 6, length.out = 4, by = 15)]
datetime <- format(seq(from = lubridate::now(), 
                        by = "3 mins",
                        length.out = length),
                    "%d.%m.%y %H:%M")
likes <-  as.integer(runif(n = length, min = 0, max = 42))
reposts <-  as.integer(runif(n = length, min = 0, max = 9))
replies <-  as.integer(runif(n = length, min = 0, max = 24))
user_followers <- as.integer(rnorm(n = length, mean = 400, sd = 200))
user_followers[user_followers < 0] <- 42
```

```{r sponsored_post}
#| eval: false
sponsored_post_A <- data.table(doc_id = 9999,
                             datetime = format(lubridate::now() - 1, "%d.%m.%y %H:%M"),
                             text = "Ad A",
                             media = NA,
                             alt_text = NA,
                             likes = 42,
                             reposts = 12,
                             replies = 0,
                             username = "Square Baby",
                             handle = "SquareBabyFood",
                             user_description = "The only organic baby food offering 💯% Daily Nutrition and a comprehensive Allergen Introduction Menu. Customized to your kiddo 👶. Fresh, organic, delivered.",
                             user_image = "https://encrypted-tbn0.gstatic.com/images?q=tbn:ANd9GcSmfrfojh946-1MF8b60I2ixREUL_6pQjAC6w&s",
                             user_followers = 133,
                             commented_post = 0,
                             sponsored = 1,
                             target = "https://squarebaby.com/",
                             condition = "A",
                             sequence = NA)

sponsored_post_B <- data.table(doc_id = 9999,
                             datetime = format(lubridate::now() - 1, "%d.%m.%y %H:%M"),
                             text = "Ad B",
                             media = NA,
                             alt_text = NA,
                             likes = 42,
                             reposts = 12,
                             replies = 0,
                             username = "Square Baby",
                             handle = "SquareBabyFood",
                             user_description = "The only organic baby food offering 💯% Daily Nutrition and a comprehensive Allergen Introduction Menu. Customized to your kiddo 👶. Fresh, organic, delivered.",
                             user_image = "https://encrypted-tbn0.gstatic.com/images?q=tbn:ANd9GcSmfrfojh946-1MF8b60I2ixREUL_6pQjAC6w&s",
                             user_followers = 133,
                             commented_post = 0,
                             sponsored = 1,
                             target = "https://squarebaby.com/",
                             condition = "A",
                             sequence = NA)

sponsored_post_C <- data.table(doc_id = 9999,
                             datetime = format(lubridate::now() - 1, "%d.%m.%y %H:%M"),
                             text = "Ad C",
                             media = NA,
                             alt_text = NA,
                             likes = 42,
                             reposts = 12,
                             replies = 0,
                             username = "Square Baby",
                             handle = "SquareBabyFood",
                             user_description = "The only organic baby food offering 💯% Daily Nutrition and a comprehensive Allergen Introduction Menu. Customized to your kiddo 👶. Fresh, organic, delivered.",
                             user_image = "https://encrypted-tbn0.gstatic.com/images?q=tbn:ANd9GcSmfrfojh946-1MF8b60I2ixREUL_6pQjAC6w&s",
                             user_followers = 133,
                             commented_post = 0,
                             sponsored = 1,
                             target = "https://squarebaby.com/",
                             condition = "A",
                             sequence = NA)

sponsored_post_D <- data.table(doc_id = 9999,
                             datetime = format(lubridate::now() - 1, "%d.%m.%y %H:%M"),
                             text = "Ad D",
                             media = NA,
                             alt_text = NA,
                             likes = 42,
                             reposts = 12,
                             replies = 0,
                             username = "Square Baby",
                             handle = "SquareBabyFood",
                             user_description = "The only organic baby food offering 💯% Daily Nutrition and a comprehensive Allergen Introduction Menu. Customized to your kiddo 👶. Fresh, organic, delivered.",
                             user_image = "https://encrypted-tbn0.gstatic.com/images?q=tbn:ANd9GcSmfrfojh946-1MF8b60I2ixREUL_6pQjAC6w&s",
                             user_followers = 133,
                             commented_post = 0,
                             sponsored = 1,
                             target = "https://squarebaby.com/",
                             condition = "A",
                             sequence = NA)
```

```{r}
create_stimuli <- function(cond = "A", fc = 1){
  ads <- 4
  safe_seq <- if ((ads - fc) >= 1) {
    seq(from = 1, to = ads - fc, by = 1)
  } else {
    integer(0)  # returns an empty integer vector if the condition is not met
  }
  stimuli <- rbind(ads_generic[safe_seq],
                   ads_focal[condition == cond, .SD[rep(1, each = fc)]],
                   data.table(doc_id,
                              datetime,
                              text = tmp$text,
                              media = tmp$image_url,
                              alt_text = tmp$alt_text,
                              likes,
                              reposts,
                              replies,
                              username = tmp$username,
                              handle = tmp$handle,
                              user_description = tmp$user_description,
                              user_image = tmp$user_image,
                              user_followers,
                              commented_post = 0,
                              sponsored = 0,
                              target = NA,
                              condition = cond,
                              sequence = sequence))
  
  setorder(stimuli, sequence)
  stimuli[, condition := paste0(cond, "_", fc)]
  stimuli[, doc_id := 1:.N]
  
  return(stimuli)
}

stimuli <- rbind(create_stimuli(cond = "A", fc = 1),
                 create_stimuli(cond = "A", fc = 2),
                 create_stimuli(cond = "A", fc = 3),
                 create_stimuli(cond = "A", fc = 4),
                 create_stimuli(cond = "B", fc = 1),
                 create_stimuli(cond = "B", fc = 2),
                 create_stimuli(cond = "B", fc = 3),
                 create_stimuli(cond = "B", fc = 4))

# rbind the same data X times.
# dt_list <- lapply(1:N, function(i) {
#     copy(stimuli)[, condition := i]
# })
# result_dt <- rbindlist(dt_list)
```


# Write Data

```{r}
data.table::fwrite(stimuli, file = "../stimuli/brazil_june.csv", sep = ";")
```

# Write Pilot Stimuli

```{r}
data.table::fwrite(rbind(create_stimuli(cond = "A", fc = 2),
                        create_stimuli(cond = "B", fc = 2)),
                  file = "../stimuli/brazil_pilot.csv")
```


# Session Info

```{r session_info}
sessionInfo()
```

